%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Colin M. Rennie} % Your name at the top
 
\moveleft.5\hoffset\centerline{115 N 4th Avenue} % Your address
\moveleft.5\hoffset\centerline{Highland Park, NJ 08904}
\moveleft.5\hoffset\centerline{+1 805 440 9589}
\moveleft.5\hoffset\centerline{colin.rennie@cs.rutgers.edu}
\moveleft.5\hoffset\centerline{www.pracsyslab.org/colin.rennie}

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\bf PhD, Department of Computer Science}  \hfill Fall 2014 - Present \\
Rutgers University, Piscataway, NJ\\
Graduate research and coursework focusing on robotics, control systems,\\ motion planning, and machine learning.

{\bf Bachelor of Science }  \hfill Fall 2006 - Spring 2011 \\
Sonoma State University, Rohnert Park, CA\\
Major in Finance, minor in Computer Science (Cum Laude)\\
Concentration on computational finance.
 
%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH AND \\TEACHING EXPERIENCE}

{\bf Graduate Research Assistant - PRACSYS Lab} \hfill Fall 2016 - Present \\
Rutgers University - Piscataway, NJ\\
Supervisor: Dr. Kostas Bekris\\
Focus on development of motion primitives for informed motion planning and control for complex Tensegrity robots. Implementation of CPG systems, iLQR trajectory optimization, and physics engine integration. 

{\bf Graduate Summer Intern - Pirate Lab} \hfill Summer 2016\\
NASA Ames Research Center - Mountain View, CA\\
Supervisor: Vytas Sunspiral\\
Summer research collaboration centered on Bayesian optimization for dynamic movement primitive/maneuver generation in a snake-like system.

{\bf Teaching Assistant - CS674: Seminar in Robotic Learning} \hfill Spring 2016 \\
Rutgers University - Piscataway, NJ\\
Professor: Dr. Abdeslam Boularias\\
Topics covered: Classical robotics, Optimal control, Kinematics, Dynamics, Reinforcement learning, Learning from demonstration, Model learning, Grasping, and Manipulation.

{\bf Teaching Assistant - CS520: Intro to Artificial Intelligence} \hfill Fall 2015 \\
Rutgers University - Piscataway, NJ\\
Professor: Dr. Abdeslam Boularias\\
Topics covered: Heuristic search, Adversarial search, Constraint satisfaction problems, Bayesian networks, Hidden markov models, Kalman and Particle filters, Markov decision processes, Linear models, Neural networks, Kernel methods, Gaussian processes, Reinforcement learning.

{\bf Research Asst. - Center for Adaptive Behavior \& Cognition} \hfill Spring 2009 \\
Max-Planck Institute for Human Development - Berlin, Germany\\
Supervisor: Dr. Henry Brighton\\
Research project using large health questionnaire response dataset, focused on reducing length while retaining predictive capabilities of responses in terms of future health risk. Side-by-side analysis of various machine learning algorithms.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%---------------------------------------------------------------------------------------- 

\section{PROFESSIONAL \\ EXPERIENCE}

{\bf Senior Analyst - Corporate Development Group} \hfill August 2012 - August 2013 \\
RPX Corporation - San Francisco, CA\\
Development of patent valuation estimation tools based on litigation, ownership, and market data. These insights were used as primary decision-making tools for the company - one of the largest purchasers of domestic Intellectual Property assets.

{\bf Analyst - Data Science Group} \hfill July 2011 - August 2012 \\
RPX Corporation - San Francisco, CA\\
Design of relational databases, external data source Input/Output protocol, and maintenance mechanisms for patent ownership, licensing, and litigation data.

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{PUBLICATIONS} 

``A Dataset for Improved RGBD-based Object Detection and Pose Estimation for Warehouse Pick-and-Place.''
\textbf{Rennie, Colin}, Rahul Shome, Kostas E. Bekris, and Alberto F. De Souza. IEEE Robotics and Automation Letters 1, no. 2: 1179-1185. (2016) [Journal version - around 33\% acceptance]

%----------------------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

\section{PRESEN-\\TATIONS} 

\sl{A Dataset for Improved RGBD-based Object Detection and Pose Estimation for Warehouse Pick-and-Place}\\
First Annual Workshop on Recovering 6D Object Pose - International Conference on Computer Vision (ICCV), 2015 [Poster]

\sl{A Dataset for Improved RGBD-based Object Detection and Pose Estimation for Warehouse Pick-and-Place}\\
IEEE International Conference on Robotics and Automation (ICRA), 2016 [Oral/Poster]

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS} 

\sl{GAANN Fellowship - Rutgers University} \hfill Fall 2014 - Spring 2015\\
\sl{Tribal Scholarship - Citizen Potawatomi Nation} \hfill Fall 2014\\
\sl{Dean's List - Sonoma State University (6 semesters)} \hfill Fall 2006 - Spring 2011\\



\end{resume}
\end{document}